\documentclass{article}

\usepackage{titlesec}
\usepackage{titling}

% set margin sizes
\usepackage[
top=0.75in,
bottom=0.75in,
left=1in,
right=1in,
]{geometry}
\usepackage{moresize}
\usepackage{enumitem}
\usepackage{url}

% sections will be Large, bold, and have a line
\titleformat{\section}  % changes what \section does
{\Large\bfseries} % formatting
{} % numbering
{0pt} % distance between numbering, and text
{} [\titlerule]

% first is space above, second is space below
\titlespacing*{\section}{0pt}{0.4\baselineskip}{0.4\baselineskip}

% subsections will be large, bold, projects and workplaces
\titlespacing*{\subsection}{0pt}{0.5\baselineskip}{0.2\baselineskip}
\titleformat{\subsection}{\large\bfseries}{}{0pt}{}

% control size of space after itemize
\setlist[itemize]{after=\vspace{-0.75em}}

\title{Resume}
\author{Benjamin LaGreca}
\thispagestyle{empty}  % removes page number at bottom

% ################################ DOCUMENT BODY ################################

\begin{document}

\begin{center}
    {\Huge\bfseries\underline{\theauthor}} \\
    \vspace{.75em}
    Email: \url{benlagreca02@gmail.com} \\
    Phone: (716) 343-4869 \\
    GitHub: \url{https://github.com/benlagreca02}
    \vspace{.25em}
    
    \bfseries Objective: Get a computer, or software engineering position
    post-graduation (Spring of 2025)
\end{center}

\vspace{-1em}

\section{Education and Academics}

    \subsection{Rochester Institute of Technology \hfill Graduation: May 2025}
    Computer Engineering, Masters \& Bachelor of Science (Dual degree Masters/Bachelors 
    program), GPA: 3.7
    % \subsection{Lockport High School \hfill Class of 2020}
    % Graduated in top 10\%. National, Science, and Mathematics Honors society member.

\section {Skills}
    \begin{itemize}[noitemsep]
        \item
            C/C++, Python, VHDL, and Dart/Flutter programming
        \item
            Linux C programming and common Linux tools including git, Vim, ip, gcc, gdb, make,
            bash, etc.
        \item
            Computer Networking and Linux Socket Programming
        \item
            ROS2, Gazebo, URDF, MoveIt and related technologies
        \item
            PyTorch for various AI applications.


        % \item
            % Soldering, Crimping, and making wire harnesses \& connectors for various 
            % applications
        % \item
            % Basic knowledge of the {\LaTeX} software system
    \end{itemize}
\section{Projects}

    \subsection{Spot Robotic Arm (Multidisciplinary Senior Design)}
    Aided in the design and production of a robotic arm for Boston Dynamic's Spot platform.
    Learned and used ROS2, Gazebo, URDF, and related tools for simulation and
    control of robotic arm.

    \subsection{Nintendo 64 Controller Adapter}
    Used an Arduino Uno to interface with and recieve data from a Nintendo 64
    controller, which sent controller data to a Arduino Pro-Micro over I2C. The
    Pro-micro emulated a generic gamepad over USB. Requried understanding of the
    communication protocol, and deep understanding of the Arduino's I/O system due 
    to timing constraints.

    \subsection{Python Biamp Network Discovery Tool}
    Wrote a Python program that discovers devices from the Tesira
    product line. The program sent a packet to a multicast address that Tesira
    devices listened for, and devices responded with relevant info. The program
    could then communicate with devices through a proprietary
    protocol. Displayed relevant in a PyQt5 generated GUI. Required low level 
    networking, PyQt5, and a strong understanding of socket programming.

    % \subsection{Simplified MIPS processor}
    % Created a simplified, Pipelined MIPS processor using VHDL in Digital Systems 
    % Design II.

\section{Experience}
    \subsection{L3Harris Systems/Software Engineering Co-op \hfill (May -
    August 2023 and 24)}
        \begin{itemize}[noitemsep]
            \item Aided in patent filing, research, implementation, and design
                of a new protocol for automatic GRE tunneling for a tactical router.
            \item Reverse engineered iproute2 package for functionality of
                netlink sockets. Used netlink sockets for communication with the
                Linux kernel to create, modify, and destroy IP GRE tunnels 
                modification.
            \item Designed and implemented Linux socket code for a new tactical
                router.
            \item Wrote XDP BPF programs and XDP socket programs to improve
                performance of a tactial router.
        \end{itemize}

    \subsection{Biamp Systems Firmware Engineering Co-op \hfill (May - December 2022)}
        \begin{itemize}[noitemsep]
            \item Implemented a C++ interface to work with PTP4L, a terminal based 
                PTP (Precision time protocol) management client for Linux.  
            \item Developed a Python program using PyQt5 GUI framework to
                discover the company's products on selected subnets.
        \end{itemize}

    \subsection{TA for Assembly and Embedded programming \hfill (2022-2023)}
    \begin{itemize}[noitemsep]
        \item Helped students with ARM assembly labs ranging from creating 
            a simple UART driver, to implementing circular FIFO queues and
            interrupt handlers
        \item Required strong debugging abilities, and a thorough understanding of 
            course material
    \end{itemize}

    % \subsection{MAHLE Electrical Component Engineer Internship\hfill (Summer 2021)}
    %     \begin{itemize}[noitemsep]
    %         \item Performed a warranty analysis process on return parts including 
    %             logging, testing, and documenting results.
    %         \item Streamlined warranty logging process with Excel VBA scripting.
    %         \item Constructed various adapters, wire harnesses, and actuator drivers 
    %             for testing and control.
    %     \end{itemize}

    % \subsection{FIRST Robotics FRC team 1507\hfill (2017-2020)}
    %     \begin{itemize}[noitemsep]
    %         \item Lead Programmer for FRC team 1507 The Warlocks
    %         \item Lead group of 5+ student programmers to program a large robot in 
    %             C++ to preform various autonomous and human driven tasks.
    %     \end{itemize}
 
    % \subsection{Lockport Caves \hfill (2018-2019)}
    % Employed as tour guide and for general maintenance. Gave hour long tour to 
    % groups of 20+ people. Required having a very flexible schedule.
        
    % \section{Classes and Labs}
    % Applied Programming in C, Digital Signal Processing, Digital Systems and Design 1 \& 2 (VHDL \& Logic Circuits), 


\end{document}
